PLAE enables quick and easy searching across one million ocular transcriptomes

### 2022-06-02 manuscript_00.Rmd
diff updates

```{r Setup..., message=FALSE, warning=FALSE, include=FALSE}
#knitr::opts_chunk$set(fig.pos = 'p') # Places figures on their own pages
knitr::opts_chunk$set(out.width = '100%', dpi=300)
library(tidyverse)
library(citr)
library(cowplot)
library(ggrepel)
library(colorspace)
library(flextable)
library(captioner)
library(glue)
data_dir_vGiga <- '/Volumes/McGaughey_S/scEiaD/'
data_dir_vPLAE <- '/Volumes/McGaughey_S/scEiaD_2022_02/'

@@

```{r}
# flip flop diff genes
down_tab <- scEiaD_2020_v01 %>% tbl('diff_testing') %>% 
  filter(Group == 'CellType (Predict)', padj < 1e-5, (log2FoldChange) < -2) %>% 
  collect() %>% 
  filter(Against == 'All', Base %in% (meta_filter %>% filter(Organ == 'Eye') %>% pull(CellType_predict) %>% unique()))

>>>>

```{r Setup..., message=FALSE, warning=FALSE, include=FALSE}
#knitr::opts_chunk$set(fig.pos = 'p') # Places figures on their own pages
knitr::opts_chunk$set(out.width = '100%', dpi=300)
library(tidyverse)
library(citr)
library(cowplot)
library(ggrepel)
library(colorspace)
library(flextable)
library(captioner)
library(glue)
data_dir_vGiga <- '~/data/scEiaD_gigascience/'
data_dir_vPLAE <- '~/data/scEiaD_2022_02/'

@@

```{r}
# flip flop diff genes
down_tab <- scEiaD_2020_v01 %>% tbl('diff_testing') %>% 
  filter(Group == 'CellType (Predict)', padj < 1e-5, (log2FoldChange) < -2) %>% 
  collect() %>% 
  filter(Against == 'All', Base %in% (meta_filter %>% filter(Organ == 'Eye') %>% pull(CellType_predict) %>% unique())) %>% mutate(k = paste(Gene, Base, sep = '_'))

diff_tab %>% mutate(k = paste(Gene, Base, sep = '_')) %>% 
  filter(k %in% down_tab$k, Base %in% c('AC/HC Precursor', 'Amacrine Cell', 'Astrocyte', 'Bipolar Cell', 'Cone', 'Early RPC',' Horizontal Cell','Late RPC','Microglia','Muller Glia', 'Neurogenic Cell', 'Photoreceptor Precursor','Retinal Ganglion Cell','Rod','Rod Bipolar Cell','RPC','RPE' )) %>% 
  arrange(padj)
```

```{r diff_difff_exp_genes, fig.height = 3, fig.width = 8, echo = F, message = F}
input <- list()
input$exp_plot_groups <- c('organism')
input$exp_plot_facet <- c('CellType_predict')
input$exp_plot_genes <- c('GNAT2 (ENSG00000134183)')
input$exp_filter_cat <- 'CellType_predict'
input$exp_filter_on <- c('AC/HC Precursor', 'Amacrine Cell', 'Astrocyte', 'Bipolar Cell', 'Cone', 'Early RPC',' Horizontal Cell','Late RPC','Microglia','Muller Glia', 'Neurogenic Cell', 'Photoreceptor Precursor','Retinal Ganglion Cell','Rod','Rod Bipolar Cell','RPC','RPE' )
input$exp_plot_ylab <- 'Mean log2(Counts + 1)'
input$exp_plot_col_num <- 16
input$exp_filter_min_cell_number <- 50

make_exp_plot(input, scEiaD_2020_v01, meta_filter)
```
